### 2015-03-13 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated report.

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Keith M. Stakes \\

@@

\headerC{
\flushright{
Daniel Madrzykowski \\
Keith M. Stakes \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

The Engineering Laboratory at National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.  One of the objectives of this program is to examine non-traditional means of fire suppression.   This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.  These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.

@@

The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement. These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression. The area of the purpose built structure used for these experiments was located on the ground floor and involved two adjoining rooms.  The fire was ignited and allowed to grow and fill the compartment with heated fire products and flame.  The developing hot gas layer spread to the adjacent room through a single doorway.  The adjacent room developed a hot gas layer and was the focus of this series of tests.

>>>>

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Keith M. Stakes \\
Craig G. Weinschenk \\

@@

\headerC{
\flushright{
Daniel Madrzykowski \\
Keith M. Stakes \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

The Engineering Laboratory at the National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.  One of the objectives of this program is to examine non-traditional means of fire suppression.   This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.  These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.

@@

The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement. The tests were conducted over a period of three days in late September of 2012 and split into a 8 different series. These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression. The area of the purpose built structure used for these experiments was located on the ground floor and involved two adjoining rooms.  The fire was ignited and allowed to grow and fill the compartment with heated fire products and flame.  The developing hot gas layer spread to the adjacent room through a single doorway.  The adjacent room developed a hot gas layer and was the focus of this series of tests.
